---
title: "R Notebook"
output: html_notebook
---


# Setup

```{r setup, include=FALSE}
# Need to set up the working directory
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/"
knitr::opts_knit$set(root.dir = workingDir)

require(tidyverse)
require(haven)
require(ggplot2)
```

```{r}
source('FEM_R/utilities.R')
```

## Data

```{r}
out.dir <- 'output/LNLY_SOCISO_TEST/'

cohort <- detailed_output_append(base.out.dir = out.dir,
                              scenario = 'ELSA_core_cohort')
nolnly <- detailed_output_append(base.out.dir = out.dir,
                              scenario = 'ELSA_nolnly_cohort')
nosociso <- detailed_output_append(base.out.dir = out.dir,
                              scenario = 'ELSA_nosociso_cohort')
```

```{r}
# save these large files in case I overwrite the output stuff
#write.csv(cohort, file = 'input_data/detailed_output/cohort_append_large.csv')
#write.csv(nolnly, file = 'input_data/detailed_output/nolnly_append_large.csv')
#write.csv(nosociso, file = 'input_data/detailed_output/nosociso_append_large.csv')

# cohort <- read.csv('input_data/detailed_output/cohort_append_large.csv')
# nolnly <- read.csv('input_data/detailed_output/nolnly_append_large.csv')
# nosociso <- read.csv('input_data/detailed_output/nosociso_append_large.csv')
```


# Baseline

```{r}
coh <- cohort

# generate lifeyear for people who have not died (also no disease and no disability)
coh$lifeyear <- 1 - coh$died
#coh$diseaseFree <- 1 - coh$anydisease
#coh$disabilityFree <- 1 - coh$disabled
# generate the number of repetitions for each person
coh$nreps <- max(coh$mcrep) + 1

# now the giant pipeline to calculate LYs, DFLYs (both) and confidence intervals
coh.sum <- coh %>%
  group_by(hhidpn, year) %>%
  mutate(nreps = n()) %>%
  group_by(hhidpn, mcrep) %>%
  summarise(n = n(),
            n_LY = sum(lifeyear),
            n_DiseaseFLY = sum(nodisease),
            n_DisabilityFLY = sum(nodisability),
            two_yr_LY = n_LY * 2,
            two_yr_DiseaseFLY = n_DiseaseFLY * 2,
            two_yr_DisabilityFLY = n_DisabilityFLY * 2,
            weight_intermed = sum(weight) / n) %>%
  group_by(hhidpn) %>%
  summarise(mean_LY_ind = mean(two_yr_LY),
            mean_DiseaseFLY_ind = mean(two_yr_DiseaseFLY),
            mean_DisabilityFLY_ind = mean(two_yr_DisabilityFLY),
            weight = mean(weight_intermed))# %>%
  
  #summarise(n = n(),
  #          LY_mean = weighted.mean(mean_LY_ind, w = weight),
  #          LY_sd = sd(mean_LY_ind),
  #          DiseaseFLY_mean = weighted.mean(mean_DiseaseFLY_ind, w = weight),
  #          DiseaseFLY_sd = sd(mean_DiseaseFLY_ind),
  #          DisabilityFLY_mean = weighted.mean(mean_DisabilityFLY_ind, w = weight),
  #          DisabilityFLY_sd = sd(mean_DisabilityFLY_ind),
  #          LY_margin = qt(p=0.975, df=n-1) * (LY_sd / sqrt(n)),
  #          LY_min = LY_mean - LY_margin,
  #          LY_max = LY_mean + LY_margin,
  #          DiseaseFLY_margin = qt(p=0.975, df=n-1) * (DiseaseFLY_sd / sqrt(n)),
  #          DiseaseFLY_min = DiseaseFLY_mean - DiseaseFLY_margin,
  #          DiseaseFLY_max = DiseaseFLY_mean + DiseaseFLY_margin,
  #          DisabilityFLY_margin = qt(p=0.975, df=n-1) * (DisabilityFLY_sd / sqrt(n)),
  #          DisabilityFLY_min = DisabilityFLY_mean - DisabilityFLY_margin,
  #          DisabilityFLY_max = DisabilityFLY_mean + DisabilityFLY_margin) %>%
  #dplyr::select(-n) %>%
  #pivot_longer(cols = everything(),
  #             names_sep = '_',
  #             names_to = c('outcome', 'statistic')) %>%
  #filter(statistic %in% c('mean', 'min', 'max', 'margin')) %>%
  #pivot_wider(values_from = 'value',
  #            names_from = 'statistic')


```


Now lets try a histogram.

```{r}
ggplot(data = coh.sum, aes(x = mean_LY_ind)) +
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density() +
  xlab('Life Years')

ggplot(data = coh.sum, aes(x = mean_DiseaseFLY_ind)) +
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density() +
  xlab('Disease Free Life Years')

ggplot(data = coh.sum, aes(x = mean_DisabilityFLY_ind)) +
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density() +
  xlab('Disability Free Life Years')
```

Now do a facet plot to show them all in one image. This will require pivoting the data to a longer format.

```{r}
coh.long <- ly_outcomes_detailed_density(cohort)

ly.density.outcomes.facet <- ggplot(data = coh.long, aes(x = years)) +
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density() +
  facet_wrap(~outcome, nrow=3) +
  xlab('Years')
ly.density.outcomes.facet

path <- 'FEM_R/Loneliness_Social_Isolation/plots/'

ggsave(filename = 'ly_dfly_density_facet.png',
      plot = ly.density.outcomes.facet,
      path = path,
      width = 10,
      height = 5)

#rm(coh.long, ly.density.outcomes.facet)
```

How about a version with Healthy Life Years instead of DFLYs.

```{r}
coh.long.hly <- ly_hly_outcomes_detailed_density(cohort)

ly.hly.density.outcomes.facet <- ggplot(data = coh.long.hly, aes(x = years)) +
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density() +
  facet_wrap(~outcome, nrow=3) +
  xlab('Years')
ly.hly.density.outcomes.facet

path <- 'FEM_R/Loneliness_Social_Isolation/plots/'

rm(coh.long.hly, ly.hly.density.outcomes.facet)
```

# Loneliness

Now do some comparison plots! In the same fashion.

```{r}
## First get the long ly and dfly outcomes for cohort and intervention scenario
coh.long <- ly_outcomes_detailed_density(cohort)
lnly.long <- ly_outcomes_detailed_density(nolnly)
#coh.long <- ly_hly_outcomes_detailed_density(cohort)
#lnly.long <- ly_hly_outcomes_detailed_density(nolnly)

# Add a column for the scenario
coh.long$scenario <- 'Baseline'
lnly.long$scenario <- 'No.Loneliness'

#coh.long <- coh.long %>% dplyr::select(-weight)
#lnly.long <- lnly.long %>% dplyr::select(-weight)

```

```{r}
#combined <- merge(coh.long, lnly.long, by = c('hhidpn', 'outcome'))
combined <- rbind(coh.long, lnly.long)

# Now ggplot with an additional group or fill aesthetic
ly.density.facet.lnlycomp <- ggplot(data = combined, aes(x = years, group = scenario, color = scenario)) +
  geom_density() +
  facet_wrap(~outcome, nrow=3) +
  xlab('Years')
ly.density.facet.lnlycomp

ggsave(filename = 'ly_dfly_density_facet_lnlycomp.png',
      plot = ly.density.facet.lnlycomp,
      path = path,
      width = 9,
      height = 5)

rm(coh.long, lnly.long, ly.density.facet.lnlycomp)
```

Excellent!! Now it would be useful to be able to show this next to the mean plots with confidence intervals.

Lets make the mean plots with confidence intervals, starting with the combined dataframe from above.
```{r}
combined.sum <- combined %>%
  dplyr::select(-hhidpn) %>%
  group_by(scenario, outcome) %>%
  summarise(n = n(),
            sd = sd(years),
            years = weighted.mean(years, w = weight),
            margin = qt(p=0.975, df=n-1) * (sd / sqrt(n))) %>%
  dplyr::select(-n, -sd)

combined.sum$scenario <- factor(combined.sum$scenario, levels = c('Baseline', 'No.Loneliness'))

mean.plot.horizontal.error <- ggplot(combined.sum, aes(x = years, y = scenario, fill = scenario)) +
  geom_col() +
  facet_wrap(~outcome, nrow = 3) +
  geom_errorbarh(aes(xmin = years - margin, xmax = years + margin),
                 height=.4) +
  xlab('Years')
mean.plot.horizontal.error

ggsave(filename = 'lnly_horizontal_mean_error.png',
       path = path,
       plot = mean.plot.horizontal.error,
       width = 9,
       height = 5)

rm(mean.plot.horizontal.error)
```

Now change plots for emphasis.

```{r}
# lnly.change <- combined.sum %>%
#   pivot_wider(names_from = 'scenario',
#               values_from = c('years', 'margin')) %>%
#   mutate(change = years_No.Loneliness - years_Baseline) %>%
#   dplyr::select(-years_No.Loneliness, -years_Baseline, -margin_Baseline) %>%
#   rename(margin = margin_No.Loneliness)
# 
# lnly.change$outcome <- factor(lnly.change$outcome, levels = c('LifeYears', 'DiseaseFree', 'DisabilityFree'))
# 
# lnly.change.horizontal <- ggplot(data = lnly.change, aes(x = change, y = reorder(outcome, ), fill = outcome)) +
#   geom_col() +
#   geom_errorbarh(aes(xmin = change - margin, xmax = change + margin),
#                  height=.4) +
#   xlab('Years')
# 
# lnly.change.horizontal
# 
# ggsave(filename = 'lnly_change_error.png',
#        path = path,
#        plot = lnly.change.horizontal,
#        width = 9,
#        height = 5)
# 
# rm(lnly.change.horizontal)
```

## Sub-Populations

### Gender

```{r}
# Now plots by gender
ly.density.facet.lnlycomp <- ggplot(data = combined, aes(x = years, group = scenario, color = scenario)) +
  geom_density() +
  facet_wrap(~outcome + male, nrow=3) +
  xlab('Years')
ly.density.facet.lnlycomp

ggsave(filename = 'lnly_density_facet_gender.png',
     plot = ly.density.facet.lnlycomp,
     path = path,
     width = 9,
     height = 5)

combined.sum <- combined %>%
  dplyr::select(-hhidpn) %>%
  group_by(scenario, outcome, male) %>%
  summarise(n = n(),
            sd = sd(years),
            years = weighted.mean(years, w = weight),
            margin = qt(p=0.975, df=n-1) * (sd / sqrt(n))) %>%
  dplyr::select(-n, -sd)

combined.sum$scenario <- factor(combined.sum$scenario, levels = c('Baseline', 'No.Loneliness'))

mean.plot.horizontal.error <- ggplot(combined.sum, aes(x = years, y = scenario, fill = scenario)) +
  geom_col() +
  facet_wrap(~outcome + male, nrow=3) +
  geom_errorbarh(aes(xmin = years - margin, xmax = years + margin),
                 height=.4) +
  xlab('Years')
mean.plot.horizontal.error

ggsave(filename = 'lnly_facet_mean_error_gender.png',
       path = path,
       plot = mean.plot.horizontal.error,
       width = 9,
       height = 5)

rm(ly.density.facet.lnlycomp, mean.plot.horizontal.error)
```

Now change plots for emphasis.

```{r}
lnly.change <- combined.sum %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('years', 'margin')) %>%
  mutate(change = years_No.Loneliness - years_Baseline) %>%
  dplyr::select(-years_No.Loneliness, -years_Baseline, -margin_Baseline) %>%
  rename(margin = margin_No.Loneliness)

gender.change.horizontal <- ggplot(data = lnly.change, aes(x = change, y = male, fill = male)) +
  geom_col() +
  facet_wrap(~outcome, nrow=3) +
  geom_errorbarh(aes(xmin = change - margin, xmax = change + margin),
                 height=.4) +
  xlab('Years') +
  ylab('Gender')

gender.change.horizontal

ggsave(filename = 'lnly_change_error_gender.png',
       path = path,
       plot = gender.change.horizontal,
       width = 9,
       height = 5)

rm(combined.sum, gender.change.horizontal)
```

### Marriage Status

```{r}
# Now plots by gender
ly.density.facet.lnlycomp <- ggplot(data = combined, aes(x = years, group = scenario, color = scenario)) +
  geom_density() +
  facet_wrap(~outcome + mstat, nrow=3) +
  xlab('Years')
ly.density.facet.lnlycomp

ggsave(filename = 'ly_dfly_density_lnly_mstat.png',
     plot = ly.density.facet.lnlycomp,
     path = path,
     width = 9,
     height = 5)

combined.sum <- combined %>%
  dplyr::select(-hhidpn) %>%
  group_by(scenario, outcome, mstat) %>%
  summarise(n = n(),
            sd = sd(years),
            years = weighted.mean(years, w = weight),
            margin = qt(p=0.975, df=n-1) * (sd / sqrt(n))) %>%
  dplyr::select(-n, -sd)

combined.sum$scenario <- factor(combined.sum$scenario, levels = c('Baseline', 'No.Loneliness'))

mean.plot.horizontal.error <- ggplot(combined.sum, aes(x = years, y = scenario, fill = scenario)) +
  geom_col() +
  facet_wrap(~outcome + mstat, nrow=3) +
  geom_errorbarh(aes(xmin = years - margin, xmax = years + margin),
                 height=.4) +
  xlab('Years')
mean.plot.horizontal.error

ggsave(filename = 'lnly_horizontal_mean_error_mstat.png',
      path = path,
      plot = mean.plot.horizontal.error,
      width = 9,
      height = 5)

lnly.change <- combined.sum %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('years', 'margin')) %>%
  mutate(change = years_No.Loneliness - years_Baseline) %>%
  dplyr::select(-years_No.Loneliness, -years_Baseline, -margin_Baseline) %>%
  rename(margin = margin_No.Loneliness)

change.plot.lnly.mstat <- ggplot(data = lnly.change, aes(x = change, y = mstat, fill = mstat)) +
  geom_col() +
  facet_wrap(~outcome, nrow=3) +
  geom_errorbarh(aes(xmin = change - margin, xmax = change + margin),
                 height=.4) +
  xlab('Years') +
  ylab('Marriage Status')
change.plot.lnly.mstat

ggsave(filename = 'lnly_change_error_mstat.png',
       path = path,
       plot = change.plot.lnly.mstat,
       width = 9,
       height = 5)

rm(ly.density.facet.lnlycomp, mean.plot.horizontal.error, combined.sum, lnly.change, change.plot.lnly.mstat)
```

### Living Alone

```{r}
# Now plots by gender
ly.density.facet.lnlycomp <- ggplot(data = combined, aes(x = years, group = scenario, color = scenario)) +
  geom_density() +
  facet_wrap(~outcome + live_alone, nrow=3) +
  xlab('Years')
ly.density.facet.lnlycomp

ggsave(filename = 'ly_dfly_lnly_liveAlone.png',
     plot = ly.density.facet.lnlycomp,
     path = path,
     width = 9,
     height = 5)

combined.sum <- combined %>%
  dplyr::select(-hhidpn) %>%
  group_by(scenario, outcome, live_alone) %>%
  summarise(n = n(),
            sd = sd(years),
            years = weighted.mean(years, w = weight),
            margin = qt(p=0.975, df=n-1) * (sd / sqrt(n))) %>%
  dplyr::select(-n, -sd)

combined.sum$scenario <- factor(combined.sum$scenario, levels = c('Baseline', 'No.Loneliness'))

mean.plot.horizontal.error <- ggplot(combined.sum, aes(x = years, y = scenario, fill = scenario)) +
  geom_col() +
  facet_wrap(~outcome + live_alone, nrow=3) +
  geom_errorbarh(aes(xmin = years - margin, xmax = years + margin),
                 height=.4) +
  xlab('Years')
mean.plot.horizontal.error

ggsave(filename = 'lnly_horizontal_mean_error_liveAlone.png',
      path = path,
      plot = mean.plot.horizontal.error,
      width = 9,
      height = 5)

lnly.change <- combined.sum %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('years', 'margin')) %>%
  mutate(change = years_No.Loneliness - years_Baseline) %>%
  dplyr::select(-years_No.Loneliness, -years_Baseline, -margin_Baseline) %>%
  rename(margin = margin_No.Loneliness)

change.plot.lnly.liveAlone <- ggplot(data = lnly.change, aes(x = change, y = live_alone, fill = live_alone)) +
  geom_col() +
  facet_wrap(~outcome, nrow=3) +
  geom_errorbarh(aes(xmin = change - margin, xmax = change + margin),
                 height=.4) +
  xlab('Years') +
  ylab('')
change.plot.lnly.liveAlone

ggsave(filename = 'lnly_change_error_liveAlone.png',
      path = path,
      plot = change.plot.lnly.liveAlone,
      width = 9,
      height = 5)

rm(ly.density.facet.lnlycomp, combined.sum, mean.plot.horizontal.error, lnly.change, change.plot.lnly.liveAlone)
```

### Carers

```{r}
ly.density.facet.lnlycomp <- ggplot(data = combined, aes(x = years, group = scenario, color = scenario)) +
  geom_density() +
  facet_wrap(~outcome + carer, nrow=3) +
  xlab('Years')
ly.density.facet.lnlycomp

ggsave(filename = 'ly_dfly_lnly_carer.png',
     plot = ly.density.facet.lnlycomp,
     path = path,
     width = 9,
     height = 5)

combined.sum <- combined %>%
  dplyr::select(-hhidpn) %>%
  group_by(scenario, outcome, carer) %>%
  summarise(n = n(),
            sd = sd(years),
            years = weighted.mean(years, w = weight),
            margin = qt(p=0.975, df=n-1) * (sd / sqrt(n))) %>%
  dplyr::select(-n, -sd)

combined.sum$scenario <- factor(combined.sum$scenario, levels = c('Baseline', 'No.Loneliness'))

mean.plot.horizontal.error <- ggplot(combined.sum, aes(x = years, y = scenario, fill = scenario)) +
  geom_col() +
  facet_wrap(~outcome + carer, nrow=3) +
  geom_errorbarh(aes(xmin = years - margin, xmax = years + margin),
                 height=.4) +
  xlab('Years')
mean.plot.horizontal.error

ggsave(filename = 'lnly_horizontal_mean_error_carer.png',
      path = path,
      plot = mean.plot.horizontal.error,
      width = 9,
      height = 5)

lnly.change <- combined.sum %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('years', 'margin')) %>%
  mutate(change = years_No.Loneliness - years_Baseline) %>%
  dplyr::select(-years_No.Loneliness, -years_Baseline, -margin_Baseline) %>%
  rename(margin = margin_No.Loneliness)

change.plot.lnly.carer <- ggplot(data = lnly.change, aes(x = change, y = carer, fill = carer)) +
  geom_col() +
  facet_wrap(~outcome, nrow=3) +
  geom_errorbarh(aes(xmin = change - margin, xmax = change + margin),
                 height=.4) +
  xlab('Years') +
  ylab('')
change.plot.lnly.carer

ggsave(filename = 'lnly_change_error_carer.png',
      path = path,
      plot = change.plot.lnly.carer,
      width = 9,
      height = 5)

rm(ly.density.facet.lnlycomp, combined.sum, mean.plot.horizontal.error, lnly.change, change.plot.lnly.liveAlone)
```


# Social Isolation

Now the same for social isolation intervention.

```{r}
#coh.long <- ly_hly_outcomes_detailed_density(cohort)
#sociso.long <- ly_hly_outcomes_detailed_density(nosociso)
coh.long <- ly_outcomes_detailed_density(cohort)
sociso.long <- ly_outcomes_detailed_density(nosociso)

# Add a column for the scenario
coh.long$scenario <- 'Baseline'
sociso.long$scenario <- 'No.Social.Isolation'

#coh.long <- coh.long %>% dplyr::select(-weight)
#sociso.long <- sociso.long %>% dplyr::select(-weight)

#combined <- merge(coh.long, lnly.long, by = c('hhidpn', 'outcome'))
combined <- rbind(coh.long, sociso.long)

# Now ggplot with an additional group or fill aesthetic
ly.density.facet.socisocomp <- ggplot(data = combined, aes(x = years, group = scenario, color = scenario)) +
  geom_density() +
  facet_wrap(~outcome, nrow=3) +
  xlab('Years')
ly.density.facet.socisocomp

ggsave(filename = 'ly_dfly_density_facet_socisocomp.png',
      plot = ly.density.facet.socisocomp,
      path = path,
      width = 9,
      height = 5)

combined.sum <- combined %>%
  dplyr::select(-hhidpn) %>%
  group_by(scenario, outcome) %>%
  summarise(n = n(),
            sd = sd(years),
            years = weighted.mean(years, w = weight),
            margin = qt(p=0.975, df=n-1) * (sd / sqrt(n))) %>%
  dplyr::select(-n, -sd)

combined.sum$scenario <- factor(combined.sum$scenario, levels = c('Baseline', 'No.Social.Isolation'))

mean.plot.horizontal.error <- ggplot(combined.sum, aes(x = years, y = scenario, fill = scenario)) +
  geom_col() +
  facet_wrap(~outcome, nrow = 3) +
  geom_errorbarh(aes(xmin = years - margin, xmax = years + margin),
                 height=.4) +
  xlab('Years')
mean.plot.horizontal.error

ggsave(filename = 'sociso_horizontal_mean_error.png',
       path = path,
       plot = mean.plot.horizontal.error,
       width = 9,
       height = 5)

rm(coh.long, sociso.long, ly.density.facet.socisocomp, combined.sum, mean.plot.horizontal.error)
```

## Change

Now change plots.

```{r}
sociso.change <- combined.sum %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('years', 'margin')) %>%
  mutate(change = years_No.Loneliness - years_Baseline) %>%
  dplyr::select(-years_No.Loneliness, -years_Baseline, -margin_Baseline) %>%
  rename(margin = margin_No.Loneliness)

sociso.change$outcome <- factor(sociso.change$outcome, levels = c('LifeYears', 'DiseaseFree', 'DisabilityFree'))

sociso.change.horizontal <- ggplot(data = sociso.change, aes(x = change, y = outcome, fill = outcome)) +
  geom_col() +
  geom_errorbarh(aes(xmin = change - margin, xmax = change + margin),
                 height=.4) +
  xlab('Years')

sociso.change.horizontal

ggsave(filename = 'sociso_change_error.png',
       path = path,
       plot = sociso.change.horizontal,
       width = 9,
       height = 5)

rm(sociso.change.horizontal)
```

## Sub-Populations

### Gender

```{r}
# Now plots by gender
ly.density.facet.socisocomp <- ggplot(data = combined, aes(x = years, group = scenario, color = scenario)) +
  geom_density() +
  facet_wrap(~outcome + male, nrow=3) +
  xlab('Years')
ly.density.facet.socisocomp

ggsave(filename = 'ly_dfly_sociso_gender.png',
     plot = ly.density.facet.socisocomp,
     path = path,
     width = 9,
     height = 5)

combined.sum <- combined %>%
  dplyr::select(-hhidpn) %>%
  group_by(scenario, outcome, male) %>%
  summarise(n = n(),
            sd = sd(years),
            years = weighted.mean(years, w = weight),
            margin = qt(p=0.975, df=n-1) * (sd / sqrt(n))) %>%
  dplyr::select(-n, -sd)

combined.sum$scenario <- factor(combined.sum$scenario, levels = c('Baseline', 'No.Social.Isolation'))

mean.plot.horizontal.error <- ggplot(combined.sum, aes(x = years, y = scenario, fill = scenario)) +
  geom_col() +
  facet_wrap(~outcome + male, nrow=3) +
  geom_errorbarh(aes(xmin = years - margin, xmax = years + margin),
                 height=.4) +
  xlab('Years')
mean.plot.horizontal.error

ggsave(filename = 'sociso_horizontal_mean_error_gender.png',
      path = path,
      plot = mean.plot.horizontal.error,
      width = 9,
      height = 5)

rm(ly.density.facet.socisocomp, mean.plot.horizontal.error)
```

Now change plots for emphasis.

```{r}
sociso.change <- combined.sum %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('years', 'margin')) %>%
  mutate(change = years_No.Social.Isolation - years_Baseline) %>%
  dplyr::select(-years_No.Social.Isolation, -years_Baseline, -margin_Baseline) %>%
  rename(margin = margin_No.Social.Isolation)

change.plot.horizontal.error <- ggplot(data = sociso.change, aes(x = change, y = male, fill = male)) +
  geom_col() +
  facet_wrap(~outcome, nrow=3) +
  geom_errorbarh(aes(xmin = change - margin, xmax = change + margin),
                 height=.4) +
  xlab('Years')
change.plot.horizontal.error

ggsave(filename = 'sociso_facet_mean_error_gender.png',
       path = path,
       plot = change.plot.horizontal.error,
       width = 9,
       height = 5)

rm(sociso.change)
```

### Marriage Status

```{r}
# Now plots by gender
ly.density.facet.socisocomp <- ggplot(data = combined, aes(x = years, group = scenario, color = scenario)) +
  geom_density() +
  facet_wrap(~outcome + mstat, nrow=3) +
  xlab('Years')
ly.density.facet.socisocomp

ggsave(filename = 'ly_dfly_density_sociso_mstat.png',
     plot = ly.density.facet.socisocomp,
     path = path,
     width = 9,
     height = 5)

combined.sum <- combined %>%
  dplyr::select(-hhidpn) %>%
  group_by(scenario, outcome, mstat) %>%
  summarise(n = n(),
            sd = sd(years),
            years = weighted.mean(years, w = weight),
            margin = qt(p=0.975, df=n-1) * (sd / sqrt(n))) %>%
  dplyr::select(-n, -sd)

combined.sum$scenario <- factor(combined.sum$scenario, levels = c('Baseline', 'No.Social.Isolation'))

mean.plot.horizontal.error <- ggplot(combined.sum, aes(x = years, y = scenario, fill = scenario)) +
  geom_col() +
  facet_wrap(~outcome + mstat, nrow=3) +
  geom_errorbarh(aes(xmin = years - margin, xmax = years + margin),
                 height=.4) +
  xlab('Years')
mean.plot.horizontal.error

ggsave(filename = 'sociso_horizontal_mean_error_mstat.png',
      path = path,
      plot = mean.plot.horizontal.error,
      width = 9,
      height = 5)

sociso.change <- combined.sum %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('years', 'margin')) %>%
  mutate(change = years_No.Social.Isolation - years_Baseline) %>%
  dplyr::select(-years_No.Social.Isolation, -years_Baseline, -margin_Baseline) %>%
  rename(margin = margin_No.Social.Isolation)

change.plot.lnly.mstat <- ggplot(data = sociso.change, aes(x = change, y = mstat, fill = mstat)) +
  geom_col() +
  facet_wrap(~outcome, nrow=3) +
  geom_errorbarh(aes(xmin = change - margin, xmax = change + margin),
                 height=.4) +
  xlab('Years')
change.plot.lnly.mstat

ggsave(filename = 'sociso_change_error_mstat.png',
       path = path,
       plot = change.plot.lnly.mstat,
       width = 9,
       height = 5)

rm(ly.density.facet.socisocomp, combined.sum, mean.plot.horizontal.error, sociso.change)
```

### Living Alone

```{r}
# Now plots by gender
ly.density.facet.socisocomp <- ggplot(data = combined, aes(x = years, group = scenario, color = scenario)) +
  geom_density() +
  facet_wrap(~outcome + live_alone, nrow=3) +
  xlab('Years')
ly.density.facet.socisocomp

ggsave(filename = 'ly_dfly_sociso_liveAlone.png',
     plot = ly.density.facet.socisocomp,
     path = path,
     width = 9,
     height = 5)

combined.sum <- combined %>%
  dplyr::select(-hhidpn) %>%
  group_by(scenario, outcome, live_alone) %>%
  summarise(n = n(),
            sd = sd(years),
            years = weighted.mean(years, w = weight),
            margin = qt(p=0.975, df=n-1) * (sd / sqrt(n))) %>%
  dplyr::select(-n, -sd)

combined.sum$scenario <- factor(combined.sum$scenario, levels = c('Baseline', 'No.Social.Isolation'))

mean.plot.horizontal.error <- ggplot(combined.sum, aes(x = years, y = scenario, fill = scenario)) +
  geom_col() +
  facet_wrap(~outcome + live_alone, nrow=3) +
  geom_errorbarh(aes(xmin = years - margin, xmax = years + margin),
                 height=.4) +
  xlab('Years')
mean.plot.horizontal.error

ggsave(filename = 'sociso_horizontal_mean_error_liveAlone.png',
      path = path,
      plot = mean.plot.horizontal.error,
      width = 9,
      height = 5)

sociso.change <- combined.sum %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('years', 'margin')) %>%
  mutate(change = years_No.Social.Isolation - years_Baseline) %>%
  dplyr::select(-years_No.Social.Isolation, -years_Baseline, -margin_Baseline) %>%
  rename(margin = margin_No.Social.Isolation)

change.plot.lnly.liveAlone <- ggplot(data = sociso.change, aes(x = change, y = live_alone, fill = live_alone)) +
  geom_col() +
  facet_wrap(~outcome, nrow=3) +
  geom_errorbarh(aes(xmin = change - margin, xmax = change + margin),
                 height=.4) +
  xlab('Years')
change.plot.lnly.liveAlone

ggsave(filename = 'sociso_change_error_liveAlone.png',
      path = path,
      plot = change.plot.lnly.liveAlone,
      width = 9,
      height = 5)

rm(ly.density.facet.socisocomp, combined.sum, mean.plot.horizontal.error, lnly.change, change.plot.lnly.liveAlone)
```

### Carer

```{r}
# Now plots by gender
ly.density.facet.socisocomp <- ggplot(data = combined, aes(x = years, group = scenario, color = scenario)) +
  geom_density() +
  facet_wrap(~outcome + carer, nrow=3) +
  xlab('Years')
ly.density.facet.socisocomp

ggsave(filename = 'ly_dfly_sociso_carer.png',
     plot = ly.density.facet.socisocomp,
     path = path,
     width = 9,
     height = 5)

combined.sum <- combined %>%
  dplyr::select(-hhidpn) %>%
  group_by(scenario, outcome, carer) %>%
  summarise(n = n(),
            sd = sd(years),
            years = weighted.mean(years, w = weight),
            margin = qt(p=0.975, df=n-1) * (sd / sqrt(n))) %>%
  dplyr::select(-n, -sd)

combined.sum$scenario <- factor(combined.sum$scenario, levels = c('Baseline', 'No.Social.Isolation'))

mean.plot.horizontal.error <- ggplot(combined.sum, aes(x = years, y = scenario, fill = scenario)) +
  geom_col() +
  facet_wrap(~outcome + carer, nrow=3) +
  geom_errorbarh(aes(xmin = years - margin, xmax = years + margin),
                 height=.4) +
  xlab('Years')
mean.plot.horizontal.error

ggsave(filename = 'sociso_horizontal_mean_error_carer.png',
      path = path,
      plot = mean.plot.horizontal.error,
      width = 9,
      height = 5)

sociso.change <- combined.sum %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('years', 'margin')) %>%
  mutate(change = years_No.Social.Isolation - years_Baseline) %>%
  dplyr::select(-years_No.Social.Isolation, -years_Baseline, -margin_Baseline) %>%
  rename(margin = margin_No.Social.Isolation)

change.plot.sociso.carer <- ggplot(data = sociso.change, aes(x = change, y = carer, fill = carer)) +
  geom_col() +
  facet_wrap(~outcome, nrow=3) +
  geom_errorbarh(aes(xmin = change - margin, xmax = change + margin),
                 height=.4) +
  xlab('Years')
change.plot.sociso.carer

ggsave(filename = 'sociso_change_error_carer.png',
      path = path,
      plot = change.plot.sociso.carer,
      width = 9,
      height = 5)

rm(ly.density.facet.socisocomp, combined.sum, mean.plot.horizontal.error, sociso.change, change.plot.sociso.carer)
```






```{r}

```

