---
title: "LYs and DFLYs from detailed out"
output: html_notebook
---




# Setup

```{r setup, include=FALSE}
# Need to set up the working directory
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/"
knitr::opts_knit$set(root.dir = workingDir)

require(tidyverse)
require(haven)
require(ggplot2)
```

```{r}
source('FEM_R/utilities.R')
```

## Data

```{r}
out.dir <- 'output/LNLY_SOCISO_TEST/'

#cohort <- detailed_output_append(base.out.dir = out.dir,
#                              scenario = 'ELSA_core_cohort')
#nolnly <- detailed_output_append(base.out.dir = out.dir,
#                              scenario = 'ELSA_nolnly_cohort')
#nosociso <- detailed_output_append(base.out.dir = out.dir,
#                              scenario = 'ELSA_nosociso_cohort')
#both <- detailed_output_append(base.out.dir = out.dir,
#                              scenario = 'ELSA_nolnly_nosociso_cohort')
```

```{r}
# save these large files in case I overwrite the output stuff
#write.csv(cohort, file = 'input_data/detailed_output/cohort_append_large.csv')
#write.csv(nolnly, file = 'input_data/detailed_output/nolnly_append_large.csv')
#write.csv(nosociso, file = 'input_data/detailed_output/nosociso_append_large.csv')
#write.csv(both, file = 'input_data/detailed_output/both_append_large.csv')

cohort <- read.csv('input_data/detailed_output/cohort_append_large.csv')
nolnly <- read.csv('input_data/detailed_output/nolnly_append_large.csv')
nosociso <- read.csv('input_data/detailed_output/nosociso_append_large.csv')
both <- read.csv('input_data/detailed_output/both_append_large.csv')
```

# Calculate Outcomes

```{r}
# Calculate LY outcomes for all scenarios
ly.coh <- ly_outcomes_from_detailed_output(cohort)
ly.lnly <- ly_outcomes_from_detailed_output(nolnly)
ly.sociso <- ly_outcomes_from_detailed_output(nosociso)
#ly.lnly.sociso <- ly_outcomes_from_detailed_output(both)
# Add scenario column for combining
ly.coh$scenario <- 'Baseline'
ly.lnly$scenario <- 'No_Loneliness'
ly.sociso$scenario <- 'No_Social_Isolation'
#ly.lnly.sociso$scenario <- 'Neither'

# Group into list and rbind all together
#ly.list <- list(ly.coh, ly.lnly, ly.sociso, ly.lnly.sociso)
ly.list <- list(ly.coh, ly.lnly, ly.sociso)
ly.all <- do.call(rbind, ly.list)

# arrange columns properly
ly.all <- ly.all %>% dplyr::select(scenario, everything())

rm(ly.lnly, ly.sociso, ly.list)
#rm(nolnly, nosociso, both)
```

# Collect and Plot

```{r}
#ly.all$scenario <- factor(ly.all$scenario, levels = c('Baseline', 'No_Loneliness', 'No_Social_Isolation', 'Neither'))
ly.all$scenario <- factor(ly.all$scenario, levels = c('Baseline', 'No_Loneliness', 'No_Social_Isolation'))
ly.all$outcome <- factor(ly.all$outcome, levels = c('LY', 'DiseaseFLY', 'DisabilityFLY'))

ly.ly <- ly.all %>% 
  filter(outcome == 'LY') %>%
  dplyr::select(-outcome)

ggplot(data = ly.ly, aes(x = scenario, y = mean, fill = scenario)) +
  geom_bar(position = 'dodge', stat = 'identity') +
  geom_errorbar(aes(ymin = min, ymax = max),
                width = 0.2) +
  labs(title = 'Life Year Comparison between Intervention Scenarios') +
  xlab("Scenario") +
  ylab("Mean Life Years")

ly.disease <- ly.all %>%
  filter(outcome == 'DiseaseFLY') %>%
  dplyr::select(-outcome)

ggplot(data = ly.disease, aes(x = scenario, y = mean, fill = scenario)) +
  geom_bar(position = 'dodge', stat = 'identity') +
  geom_errorbar(aes(ymin = min, ymax = max),
                width = 0.2) +
  labs(title = 'Disease Free Life Year Comparison between Intervention Scenarios') +
  xlab("Scenario") +
  ylab("Mean Disease Free Life Years")

ly.disability <- ly.all %>%
  filter(outcome == 'DisabilityFLY') %>%
  dplyr::select(-outcome)

ggplot(data = ly.disability, aes(x = scenario, y = mean, fill = scenario)) +
  geom_bar(position = 'dodge', stat = 'identity') +
  geom_errorbar(aes(ymin = min, ymax = max),
                width = 0.2) +
  labs(title = 'Disability Free Life Year Comparison between Intervention Scenarios') +
  xlab("Scenario") +
  ylab("Mean Disability Free Life Years")

rm(ly.ly, ly.disability, ly.disease)
```

## Change

```{r}
# Now do change plots starting with the ly.all object
ly.change <- ly.all %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('mean', 'min', 'max', 'margin')) %>%
  mutate(L_change = mean_No_Loneliness - mean_Baseline,
         S_change = mean_No_Social_Isolation - mean_Baseline,
         L_min = L_change - margin_No_Loneliness,
         L_max = L_change + margin_No_Loneliness,
         S_min = S_change - margin_No_Social_Isolation,
         S_max = S_change + margin_No_Social_Isolation) %>%
  dplyr::select(outcome, contains('L_'), contains('S_'), -contains('No_Social_Isolation')) %>%
  pivot_longer(cols = L_change:S_max,
               names_sep = '_',
               names_to = c('scenario', 'statistic'),
               values_to = 'LifeYears') %>%
  pivot_wider(names_from = 'statistic',
              values_from = 'LifeYears')

ly.change$scenario <- factor(ly.change$scenario, levels = c('L', 'S'))
  
combined.plot <- ggplot(data = ly.change, aes(x = scenario, y = change, fill=scenario)) +
  geom_col() +
  facet_wrap(~outcome) +
  geom_errorbar(aes(ymin = min, ymax = max)) +
  labs(title = 'Life Years, Disease Free Life Years, and Disability Free Life Years') +
  xlab('Scenario') +
  ylab('Change (years)')

combined.plot


path <- 'FEM_R/Loneliness_Social_Isolation/plots'

ggsave(filename = 'ly_dfly_facet_scen_confints.png',
      plot = combined.plot,
      path = path,
      width = 9,
      height = 6)

#rm(ly.change, combined.plot)
```

# Total Burden: Loneliness

Now for actual presentation plots. First up is the total burden of loneliness. I want firstly these plots for the whole population (with confidence intervals), and then we can look at specific sub-groups. 

## Full Population

```{r}
# start with the cohort and nolnly dataframes
#coh <- cohort
#nol <- nolnly

# get LifeYear, Disease, and Disability Free life years
ly.coh <- ly_outcomes_from_detailed_output(cohort)
ly.lnly <- ly_outcomes_from_detailed_output(nolnly)

ly.coh
ly.lnly

```

### Full Plot LYs

```{r}
# First add scenario information and combine
ly.coh$scenario <- 'Baseline'
ly.lnly$scenario <- 'No.Loneliness'
nolnly.comp <- rbind(ly.coh, ly.lnly)
nolnly.comp <- nolnly.comp %>% 
  dplyr::select(scenario, everything())

# Now pivot and calculate the difference
comp <- nolnly.comp %>%
  dplyr::select(-min, -max) %>%
  pivot_wider(names_from = c(scenario),
              values_from = c(mean, margin)) %>%
  mutate(change = mean_No.Loneliness - mean_Baseline) %>%
  pivot_longer(cols = mean_Baseline:margin_No.Loneliness,
               names_to = c('Statistic', 'Scenario'),
               names_sep = '_',
               values_to = 'Years')

comp.LY <- nolnly.comp %>%
  dplyr::select(-min, -max) %>%
  filter(outcome == 'LY')

ggplot(data = comp.LY, aes(x = scenario, y = mean, fill = scenario)) +
  geom_col() +
  geom_errorbar(aes(ymin = mean - margin, ymax = mean + margin))
```

### Change Plot LYs

```{r}
# Now do change plots starting with the ly.all object
ly.change <- comp %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('mean', 'min', 'max', 'margin')) %>%
  mutate(L_change = mean_No_Loneliness - mean_Baseline,
         S_change = mean_No_Social_Isolation - mean_Baseline,
         LS_change = mean_Neither - mean_Baseline,
         L_min = L_change - margin_No_Loneliness,
         L_max = L_change + margin_No_Loneliness,
         S_min = S_change - margin_No_Social_Isolation,
         S_max = S_change + margin_No_Social_Isolation,
         LS_min = LS_change - margin_Neither,
         LS_max = LS_change + margin_Neither) %>%
  dplyr::select(outcome, contains('L_'), contains('S_'), contains('LS_'), -contains('No_Social_Isolation')) %>%
  pivot_longer(cols = L_change:LS_max,
               names_sep = '_',
               names_to = c('scenario', 'statistic'),
               values_to = 'LifeYears') %>%
  pivot_wider(names_from = 'statistic',
              values_from = 'LifeYears')
```


```{r}
comp.plot <- comp %>%
  filter(Statistic == 'margin') %>%
  dplyr::select(-Statistic) %>%
  rename(margin = Years) %>%
  dplyr::select(outcome, Scenario, change, margin) %>%
  filter(Scenario == 'No.Loneliness') %>%
  dplyr::select(-Scenario)

comp.plot$outcome <- factor(comp.plot$outcome, levels = c('LY', 'DisabilityFLY', 'DiseaseFLY'))

ggplot(data = comp.plot, aes(x = outcome, y = change)) +
  geom_col()
```



Rural areas with higher proportions of older people also have cuts to services that keep them more isolated. I.e. bus services, high streets shops, etc.

Get some census information and try to plot a quick and dirty map. This would tick the geography box and could be a good crescendo to the presentation, highlighting the need for targeted spatial policy interventions.










```{r}

```

