---
title: "R Notebook"
output: html_notebook
---

Going to have a go at producing estimates of disease free life years and disability free life years.

To do this we need to use the 'disabled' and 'anydisease' variables that are defined in ELSA_vars.txt.

First setup and reading in data files.

# Setup
```{r "setup", include=FALSE}
# Need to set up the environment
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/output/COMPLETE/"
knitr::opts_knit$set(root.dir = workingDir)

require(tidyverse)
require(haven)
#require(reshape2)
require(ggplot2)
#require(ggpubr)
#require(plyr)
#require(data.table)

```

# Read in Data
```{r}
## Read in all the data
# Baselines
#base <- read_dta('ELSA_core_base/ELSA_core_base_summary.dta')
cohort <- read_dta('ELSA_core_cohort/ELSA_core_cohort_summary.dta')

# Hearte (cohort and pop)
#heart_c <- read_dta('ELSA_core_remove_hearte_c/ELSA_core_remove_hearte_c_summary.dta')
#heart_p <- read_dta('ELSA_core_remove_hearte_p/ELSA_core_remove_hearte_p_summary.dta')

# Smoking (cohort)
#smok <- read_dta('ELSA_core_remove_smoken/ELSA_core_remove_smoken_summary.dta')

# BMI (cohort)
#nomorbid <- read_dta('ELSA_core_nomorbid/ELSA_core_nomorbid_summary.dta')
#obese2 <- read_dta('ELSA_core_noobese2/ELSA_core_noobese2_summary.dta')
#obese1 <- read_dta('ELSA_core_noobese1/ELSA_core_noobese1_summary.dta')

# Drinking (pop)
#nodrink_p <- read_dta('ELSA_core_remove_drink_p/ELSA_core_remove_drink_p_summary.dta')
#nodrink_c <- read_dta('ELSA_core_remove_drink_c/ELSA_core_remove_drink_c_summary.dta')
#noBadDrink <- read_dta('ELSA_core_remove_problem_drink_p/ELSA_core_remove_problem_drink_p_summary.dta')
```

# IDEA!!!

Think we need to get the average of disabled var and multiply by the total endpop of corresponding year.
This way, we'll calculate the average number of diseased (or disabled) years, and then we can do the 
opposite calculation to get non-diseased or non-disabled. 

Got this idea from looking at the `summary_file_statistics.do` file in input_data/detailed_output/, lines 72-77. Check out the whole idea, this script goes:

- Calculate total_lifeyear for each person m_endpop_xxx * 2
- Calculate summed_total_lifeyear for whole population ( sum(total_lifeyear) )
- Calculate average_lifeyear (summed_total_lifeyear / m_endpop_xxx)

Same can be done for disability free life years and disease free life years, see script for details.

## LifeYears

### Functions
```{r}
cohortLifeyear <- function(c) {
  c.tot.lfyrs <- c$m_endpop_all * 2
  c.sum.tot.lfyrs <- sum(c.tot.lfyrs)
  c.avg.lfyr <- c.sum.tot.lfyrs / c$m_endpop_all[1]
  return(c.avg.lfyr)
}

lifeyearComparison <- function(c, i, int.name) {
  
  c.avg.lfyr <- cohortLifeyear(c)
  
  i.avg.lfyr <- cohortLifeyear(i)
  
  print(int.name)
  print(paste('Cohort Average Lifeyears:        ', signif(c.avg.lfyr, digits=4)))
  print(paste('Intervention Average Lifeyears:  ', signif(i.avg.lfyr, digits=4)))
  print(paste('Increase:                        ', signif(x = (i.avg.lfyr - c.avg.lfyr), digits=4)))
}

diseaseVarLifeyear <- function(c, var) {
  
  prevVar <- paste0('p_', var, '_all')
  
  c.tot.var.lfyrs <- c[prevVar] * c$m_endpop_all * 2
  c.sum.var.lfyrs <- sum(c.tot.var.lfyrs)
  c.avg.var.lfyrs <- c.sum.var.lfyrs / c$m_endpop_all[1]
  
  print(paste0(var, ':    ', signif(c.avg.var.lfyrs, digits=4)))
}

```

### Cohort
```{r}
# Cohort life years
c <- cohort_full
c.ly <- cohortLifeyear(c)
print(paste0('Cohort Life Years: ', signif(c.ly, digits=4)))
print('-------------------')

# Cohort disease life years
diseaseVarLifeyear(c, 'cancre')
diseaseVarLifeyear(c, 'diabe')
diseaseVarLifeyear(c, 'hearte')
diseaseVarLifeyear(c, 'lunge')
diseaseVarLifeyear(c, 'hibpe')
diseaseVarLifeyear(c, 'stroke')
diseaseVarLifeyear(c, 'alzhe')
diseaseVarLifeyear(c, 'demene')
#diseaseVarLifeyear(c, 'smoken')
#diseaseVarLifeyear(c, 'drink')
#diseaseVarLifeyear(c, 'heavy_smoker')
#diseaseVarLifeyear(c, 'problem_drinker')
```

### Smoking
```{r}
# Cohort
c <- cohort
# No smoking
s <- smok

lifeyearComparison(c, s, 'No Smoking')
```

### Heart Disease
```{r}
# Cohort
c <- cohort
# No Heart Disease
h <- heart_c

lifeyearComparison(c, h, 'No Heart Disease')
```

### Obesity
```{r}
c <- cohort
o <- obese1
lifeyearComparison(c, o, 'No Obesity')
```

### Drink
```{r}
c <- cohort
d <- nodrink_c
lifeyearComparison(c, d, 'No Drink')
```


## Disability

### Functions
```{r}
disabilityLifeYearsCohort <- function(c) {
  total_dis <- c$a_disabled_all * c$m_endpop_all
  sum_tot_dis <- sum(total_dis)
  avg_dis <- sum_tot_dis / c$m_endpop_all[1]
  return(avg_dis)
}

disabilityLifeYearComp <- function(c, i, int.name) {
  c.avg.dis <- disabilityLifeYearsCohort(c)
  i.avg.dis <- disabilityLifeYearsCohort(i)
  print(int.name)
  print(paste('Cohort Average Lifeyears:        ', signif(c.avg.dis, digits=4)))
  print(paste('Intervention Average Lifeyears:  ', signif(i.avg.dis, digits=4)))
  print(paste('Increase:                        ', signif(x = (i.avg.dis - c.avg.dis), digits=4)))
}

disabilityFreeLifeYearsCohort <- function(c) {
  total_disfree <- c$a_not_disabled_all * c$m_endpop_all
  sum_tot_disfree <- sum(total_disfree)
  avg_disfree <- sum_tot_disfree / c$m_endpop_all[1]
  return(avg_disfree)
}

disabilityFreeLifeYearsComp <- function(c, i, int.name) {
  c.avg.dis <- disabilityFreeLifeYearsCohort(c)
  i.avg.dis <- disabilityFreeLifeYearsCohort(i)
  print(int.name)
  print(paste('Cohort Average Disability Free Lifeyears:        ', signif(c.avg.dis, digits=4)))
  print(paste('Intervention Average Disability Free Lifeyears:  ', signif(i.avg.dis, digits=4)))
  print(paste('Increase:                                        ', signif(x = (i.avg.dis - c.avg.dis), digits=4)))
}

disVarDFLY <- function(c, var) {
  prevVar <- paste0('p_', var, '_all')
  
  c.tot.var.dfly <- c[prevVar] * c$a_not_disabled_all * c$m_endpop_all
  c.sum.var.dfly <- sum(c.tot.var.dfly)
  c.avg.var.dfly <- c.sum.var.dfly / c$m_endpop_all[1]
  
  print(paste0(var, ':    ', signif(c.avg.var.dfly, digits=4)))
}
```

### Cohort
```{r}
# Cohort life years
c <- cohort
c.dly <- disabilityLifeYearsCohort(c)
print(paste0('Cohort Disabled Life Years: ', signif(c.dly, digits=4)))
print('-------------------')
c.dfly <- disabilityFreeLifeYearsCohort(c)
print(paste0('Cohort Disability Free Life Years: ', signif(c.dfly, digits=4)))
print('-------------------')

# Cohort disability life years
disVarDFLY(c, 'cancre')
disVarDFLY(c, 'diabe')
disVarDFLY(c, 'hearte')
disVarDFLY(c, 'lunge')
disVarDFLY(c, 'hibpe')
disVarDFLY(c, 'stroke')
disVarDFLY(c, 'alzhe')
disVarDFLY(c, 'demene')
#disVarDFLY(c, 'smoken')
#disVarDFLY(c, 'drink')
#disVarDFLY(c, 'heavy_smoker')
#disVarDFLY(c, 'problem_drinker')
```


### Smoking
```{r}
c <- cohort
# No Heart Disease
s <- smok

disabilityFreeLifeYearsComp(c, s, 'No Smoking')
```

### Heart Disease

```{r}
c <- cohort
# No Heart Disease
h <- heart_c
disabilityFreeLifeYearsComp(c, h, 'No Heart Disease')
cohortLifeyear(c)
```

### Not Disabled
```{r}
c <- cohort
# No Heart Disease
h <- heart_c

disabilityFreeLifeYearsComp(c, h, 'No Heart Disease')
```

```{r}
c <- cohort
s <- smok

disabilityFreeComparison(c, s, 'No Smoking')
```













# Defunkt
## Disability Free Life Years

Going to attempt disease free first.

What we are looking for is a change in the total number of people with no diseases. i.e. change in n_anydisease_all

Bryan said to 'sum it up for the whole duration of the simulation'. I don't know what this means, but if I have a good go at it now I can always ask him next time we meet.

```{r}
c <- cohort
s <- smok

cSel <- c %>%
          select('year', n_disabled_all, m_endpop_all) %>%
          dplyr::rename('disabled' = n_disabled_all, 'total' = m_endpop_all)

sSel <- s %>%
          select('year', n_disabled_all, m_endpop_all) %>%
          dplyr::rename('disabled' = n_disabled_all, 'total' = m_endpop_all)

#combined <- merge(cSel, sSel, by='year')

# Add source and rbind
cSel$source <- 'cohort'
sSel$source <- 'intervention'

combined <- rbind(cSel, sSel)

ggplot(combined, aes(x = year, y = disabled, color = source)) +
  geom_line()
```

The graph above shows why we cannot rely on graphical interpretations of the 'n_' var alone.

Let's try to get the number of disabled years per person.

```{r}
cSel2 <- cSel
sSel2 <- sSel

# Population is in millions initially
cSel2$total <- cSel2$total * 1000000
sSel2$total <- sSel2$total * 1000000

cSel2$dis_by_person <- cSel2$disabled / cSel2$total
sSel2$dis_by_person <- sSel2$disabled / sSel2$total

combined2 <- rbind(cSel2, sSel2)

ggplot(data = combined2, aes(x = year, y = dis_by_person, color = source)) +
  geom_line()

```

### Try again, this time with the correct variable (not disabled)

```{r}
c <- cohort
s <- smok

cSel <- c %>%
          select('year', n_not_disabled_all, m_endpop_all) %>%
          dplyr::rename('disabled' = n_not_disabled_all, 'total' = m_endpop_all)

sSel <- s %>%
          select('year', n_not_disabled_all, m_endpop_all) %>%
          dplyr::rename('disabled' = n_not_disabled_all, 'total' = m_endpop_all)

#combined <- merge(cSel, sSel, by='year')

# Add source and rbind
cSel$source <- 'cohort'
sSel$source <- 'intervention'

combined <- rbind(cSel, sSel)

ggplot(combined, aes(x = year, y = disabled, color = source)) +
  geom_line()
```

```{r}
cSel2 <- cSel
sSel2 <- sSel

# Population is in millions initially
cSel2$total <- cSel2$total * 1000000
sSel2$total <- sSel2$total * 1000000

cSel2$dis_by_person <- cSel2$disabled / cSel2$total
sSel2$dis_by_person <- sSel2$disabled / sSel2$total

combined2 <- rbind(cSel2, sSel2)

ggplot(data = combined2, aes(x = year, y = dis_by_person, color = source)) +
  geom_line()

```


```{r}

```

