---
title: "R Notebook"
output: html_notebook
---

This script will attempt a couple of things using detailed output data files. We will attempt:
- Disability free life years (and disease free)
- Treatment on the treated analysis

First we're going to have a go at replicating the file tot_test.do, saved in E_FEM_clean/Bryan_scripts

```{r "setup", include=FALSE}
# Need to set up the environment
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/"
knitr::opts_knit$set(root.dir = workingDir)

require(tidyverse)
require(haven)
#require(reshape2)
require(ggplot2)
#require(ggpubr)
#require(plyr)
#require(data.table)

rm(workingDir)
```

Setup is complete, so let's read in some of the data files.

We are using detailed output, so need the appended data files that should be in the output folders. 

```{r}
#cohort <- read_dta('ELSA_core_cohort/ELSA_core_cohort_append.dta')
#heart <- read_dta('ELSA_core_remove_hearte_c/ELSA_core_remove_hearte_c_append.dta')
#smok <- read_dta('ELSA_core_remove_smoken/ELSA_core_remove_smoken_append.dta')

path <- 'input_data/detailed_output/'

cohort <- read_dta(paste0(path, 'ELSA_cohort_append.dta'))
mup <- read_dta(paste0(path, 'ELSA_alcInt_cohort_append.dta'))
```

Now start with the cohort file, and try to calculate a host of things like life years, dflys, and other things like that.

Generate stats for lung disease and heart disease.

```{r}

# generate flag for initial wave with disease and year died (if known)
new.c <- cohort %>%
          group_by(hhidpn, mcrep) %>%
          arrange(year, .by_group = TRUE) %>%
          mutate(hearte_init = min(year[hearte == 1]), hearte_died = max(year[hearte == 1])) %>%
          mutate(diabe_init = min(year[diabe == 1]), diabe_died = max(year[diabe == 1]))



# Replace all infinite values with 0 (infinites generated in mutate calls above)
new.c$hearte_init[is.infinite(new.c$hearte_init)] <- 0
new.c$hearte_died[is.infinite(new.c$hearte_died)] <- 0
new.c$diabe_init[is.infinite(new.c$diabe_init)] <- 0
new.c$diabe_died[is.infinite(new.c$diabe_died)] <- 0

# now generate flag variable if 


#rm(new)
```






## Using output from stata script treatment_on_treated.do or some version of it

```{r}

aData <- read_dta('/home/luke/Documents/E_FEM_clean/E_FEM/input_data/detailed_output/tot/base_treated_merged_smoken_tot_test.dta')

```

### Whole Population
```{r}

all <- aData %>%
        summarise(improv.ly = mean(improved_lifeyears), improv.dfly = mean(improved_dflys))

all

```

```{r}
all2 <- aData %>%
          summarise(base.ly = mean(total_lifeyears_basecase), int.ly = mean(total_lifeyears),
                    base.dfly = mean(total_dflys_basecase), int.dfly = mean(total_dflys))

all2
```


### By Education
```{r}

educ <- aData %>%
          group_by(educ) %>%
          summarise(improv.ly = mean(improved_lifeyears), improv.dfly = mean(improved_dflys))

educ



```

```{r}
educ2 <- aData %>%
          group_by(educ) %>%
          summarise(base.ly = mean(total_lifeyears_basecase), int.ly = mean(total_lifeyears),
                    base.dfly = mean(total_dflys_basecase), int.dfly = mean(total_dflys))

educ2
```

