---
title: "R Notebook"
output: html_notebook
---

This notebook is for debugging purposes. The current plan is to write a Make rule for running this notebook automatically at the end of a model run.

The purpose of this notebook is:
- Present the T-tests altogether in one document.
- Present all transition models in same document.
- Add visualisation for cross-validation 2 output

Do all this for both minimal models and cross-validation.

```{r setup, include=FALSE}
# Need to set up the environment
workingDir <- "/home/luke/Documents/E_FEM_clean/E_FEM/output/"
knitr::opts_knit$set(root.dir = workingDir)

require(tidyverse)
require(formattable)
#require(haven)
#require(reshape2)
#require(ggplot2)
#require(gridExtra)

```

```{r include=FALSE}

# Specify a function to rename the dataframes, so we can run in an sapply()
rename_first_var <- function(testCSV, prefix) {
  testCSV[,1] <- paste0(testCSV[,1], '_', prefix)
  return(testCSV)
}

```


First, we will collect and present all the T-tests together. We will add the prefix 'min_' or 'cv_' onto the variable names so we don't get mixed up.

```{r}
# names for T-tests directory and filename stem
min <- "ELSA_minimal/T-tests/"
stem <- "minimal_all_waves_"

# Read in all the T-test csv files
min_uw <- read.csv(paste0(min, stem, "unweighted.csv"))
min_demog <- read.csv(paste0(min, stem, "demog.csv"))
min_binhlth <- read.csv(paste0(min, stem, "binhlth.csv"))
min_binecon <- read.csv(paste0(min, stem, "binecon.csv"))
min_risk <- read.csv(paste0(min, stem, "risk.csv"))

# Collect in a list to run a list apply
min_list <- list(min_uw, min_demog, min_binhlth, min_binecon, min_risk)
# Add prefix 'min_' onto every variable name for clarity
min_list <- lapply(min_list, rename_first_var, prefix='min')

```

```{r}
# names for T-tests directory and filename stem
CV1 <- "ELSA_CrossValidation1/T-tests/"
stem <- "CV1_all_waves_"
# Read in files
cv_uw <- read.csv(paste0(CV1, stem, "unweighted.csv"))
cv_demog <- read.csv(paste0(CV1, stem, "demog.csv"))
cv_binhlth <- read.csv(paste0(CV1, stem, "binhlth.csv"))
cv_binecon <- read.csv(paste0(CV1, stem, "binecon.csv"))
cv_risk <- read.csv(paste0(CV1, stem, "risk.csv"))
# Now collect into list and rename vars for clarity
cv_list <- list(cv_uw, cv_demog, cv_binhlth, cv_binecon, cv_risk)
cv_list <- lapply(cv_list, rename_first_var, prefix='CV')
```

Both Minimal and Cross-validation T-tests are now renamed and collected into a separate list object each. We will now combine like tests together (i.e. demog with demog, binhlth with binhlth).

```{r include=FALSE}
# Set up vector with all p-value column names. Require these for table formatting
pValNames <- c('p_value_wave3', 'p_value_wave4', 'p_value_wave5', 'p_value_wave6', 'p_value_wave7', 'p_value_wave8')
```


### Unweighted (died)
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
uw <- rbind(min_list[[1]], cv_list[[1]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
uw <- arrange(uw, variable)
#uw
formattable(uw, 
            align = c('l', rep('r', ncol(uw) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Demographics
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
demog <- rbind(min_list[[2]], cv_list[[2]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
demog <- arrange(demog, variable)
formattable(demog, 
            align = c('l', rep('r', ncol(demog) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Binary Health
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
binhlth <- rbind(min_list[[3]], cv_list[[3]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
binhlth <- arrange(binhlth, variable)
formattable(binhlth, 
            align = c('l', rep('r', ncol(binhlth) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Binary Economic
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
binecon <- rbind(min_list[[4]], cv_list[[4]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
binecon <- arrange(binecon, variable)
formattable(binecon, 
            align = c('l', rep('r', ncol(binecon) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Risk Behaviours
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
risk <- rbind(min_list[[5]], cv_list[[5]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
risk <- arrange(risk, variable)
formattable(risk, 
            align = c('l', rep('r', ncol(risk) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```

```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
risk <- rbind(min_list[[5]], cv_list[[5]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
risk <- arrange(risk, variable)
formattable(risk, 
            align = c('l', rep('r', ncol(risk) - 1)),
            list(area(col=pValNames) ~ color_tile('transparent', 'red')))
```

